---
title: "COD Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: JcuWB
#### Pilot: Michael Henry Tessler
#### Co-pilot: Tom Hardwicke  
#### Start date: 04/17/2017
#### End date: [Insert end date - use US format]   

-------

#### Methods summary: 
The authors are interested in the "endowment effect" in three-to-four-year-olds.
Specifically, they examine the change in subject valuation (herafter, "value change") of two identical objects which differ in their owner (child vs. experimenter).
They predict an interaction of object-owner with a priming manipulation which focuses the child on her/hisself (vs. focusing on others vs. neural control).
When children are given a distractor task (between the two valuations) that makes them focus on themselves (by drawing a picture of themselves), they will display a greater endowement effect.

------

#### Target outcomes: 

Information about the statistical model (Section 2.2.1):

> To examine the effects of priming on value-change for the two identical endowment toys, a mixed ANCOVA was conducted. Toy owner (child or experimenter) was entered as a repeated measures factor and picture type (self-focus, other- focus, neutral-focus) and gender were entered as a between sub- jects factors. Additionally, child age was normalized and entered as a covariate into the model.

Main results (Section 2.3):

> We found a significant interaction between picture construction condition and toy owner (F(2, 53) = 4.83, p = 0.01, View the MathML source). Specifically, following self-focus, children increased the value of their own toy (M = 0.95, 95% CI = [0.38, 1.52]) but not the experimenter’s toy (M = −0.07, 95% CI = [−0.74, 0.59], t(19) = 3.56, p = 0.01, d = 0.81, Bonferroni corrected). The opposite pattern of responses were observed in the other-focus condition, in which children valued the experimenter’s toy higher (M = 0.86, 95% CI = [0.20, 1.51]), but not their own toy (M = 0.17, 95% CI = [−0.39, 0.73]) - although this effect was not statistically significant (t(19) = −1.61, p = 0.36, d = 0.48, Bonferroni corrected). There was no significant effect of toy owner in the neutral-focus condition (Mchild = 0.89, 95% CIchild = [0.31, 1.46], Mexperimenter = 0.71, 95% CIexperimenter = [0.04, 1.38], t(19) = 0.48, p = 0.64, d = 0.13). The mean value change scores for each condition as a function of toy owner are presented in Fig. 2. We found no significant main effects of types of picture type (Mself = 0.44, 95% CIself = [−0.04, 0.91], Mother = 0.51, 95% CIother = [0.04, 0.98], Mneutral = 0.80, 95% CIneutral = [0.32, 1.28], F(2, 53) = 0.61, p = 0.55, View the MathML source) or toy owner (Mchild = 0.67, 95% CIchild = [0.34, 0.99], Mexperimenter = 0.50, 95% CIexperimenter = [0.12, 0.89], F(1, 53) = 0.55, p = 0.46, View the MathML source). A significant effect of age was observed (F(1, 53) = 7.68, p = 0.01, View the MathML source), indicating that older children increased their valuations more than younger children regardless of toy owner or picture condition. No significant effect of gender (F(1, 53) = 0.46, p = 0.50, View the MathML source), and no significant interactions involving gender or age were observed (Fs < 2.69, ps > 0.11, etc.).



------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
#library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CODreports) # custom report functions
library(ez)

to.n <- function(fctr){
  return(as.numeric(as.character(fctr)))
}
```

## Step 2: Load data

```{r}
df <- read.csv("data/data.csv")
```

This data frame has 18 variables: 
- participant ID, gender, age, experiment #, prime_type (manipulation), 
- baseline scores for the endowment object(s) (reported in text to be the same for the identical objects for all children), neutral objects, 
- post scores for the endowment object given to the child, experimenter, and for the neutral object
- prime_time is the amount of time spent on the priming / distractor task
- pronouns is number of pronouns of either second person (You, for self-priming) and third person (They, for other priming) in their respective conditions
- I'm not sure what "swap" is
- change scores (post - baseline)

## Step 3: Tidy data

```{r}
df.tidy <- df %>% filter(study == 1) %>%
  separate(prime_time, into =c('min', 'sec'), sep = "min") %>%
  select(-unowned_post, -unowned_change) %>% # not used in expt 1
  separate(age, into = c("year", "month"), sep = "y") %>%
  mutate(sec = gsub("sec", "", sec),
         sec = as.numeric(sec),
         min = as.numeric(min),
         month = as.numeric(gsub("m", "", month)),
         year = as.numeric(year),
         age_in_months = year*12 + month,
         prime_time_seconds = min*60 + sec,
         neutral_baseline = to.n(neutral_baseline),
         experimenter_post = to.n(experimenter_post),
         neutral_post = to.n(neutral_post),
         experimenter_change = to.n(experimenter_change),
         neutral_change = to.n(neutral_change),
         child_baseline = endowment_baseline, # since endowment baseline is the same for both what will become the child's and the experimenter's toys, i create new variables representing this
         experimenter_baseline = endowment_baseline) %>%
  select(-endowment_baseline) %>%
  gather(object, response, ends_with("_baseline"), ends_with("_post"), ends_with("_change")) %>%
  separate(object, into = c("object", "scoringPeriod"))
```

Check the "raw" change scores by subtracting baseline from post

```{r}
df.tidy %>%
  spread(scoringPeriod, response) %>%
  mutate(derivedChange = post - baseline,
         diff = change - derivedChange) %>%
  summarize(totalDeviation = sum(diff))
```
The "change" scores reported in the raw data are the same as "post" - "baseline". Good.

## Step 3: Preprocessing

For ANCOVA, age is normalized
```{r}
mean_age = mean(df.tidy$age_in_months)
sd_age = sd(df.tidy$age_in_months)
df.tidy <- df.tidy %>% 
  mutate(age_normalized = (age_in_months - mean_age) / sd_age)
```


## Step 4: Run analysis

### Descriptive statistics


```{r reported_descriptives}
reported_descriptives <- list(
  self_focus = list(
    child_change = 
      list( mean = 0.95, ci_low = 0.38, ci_high = 1.52), 
    experimenter_change =
      list( mean = -0.07, ci_low = -0.74, ci_high = 0.59)
  ),
  other_focus = list(
    child_change = 
      list( mean = 0.17, ci_low = -0.39, ci_high = 0.73), 
    experimenter_change =
      list( mean = 0.86, ci_low = 0.2, ci_high = 1.51)
  ),
  neutral_focus = list(
    child_change = 
      list( mean = 0.89, ci_low = 0.31, ci_high = 1.46), 
    experimenter_change =
      list( mean = 0.71, ci_low = 0.04, ci_high = 1.38)
  ),
  picture_types = list(
    self = 
     list(mean = 0.44, ci_low = -0.04, ci_high = 0.91),
   other = 
     list(mean = 0.51, ci_low = 0.04, ci_high = 0.98),
   neutral = 
     list(mean = 0.80, ci_low = 0.32, ci_high = 1.28)
   ),
  toy_owner = list(
    child = list(mean = 0.67, ci_low = 0.34, ci_high = 0.99),
    experimenter = list(mean = 0.5, ci_low = 0.12, ci_high = 0.89)
  )
)
```



```{r descriptives_prime_typeXobject}
df.object.prime_type.summary <- df.tidy %>%
  spread(scoringPeriod, response) %>%
  group_by(object, prime_type) %>%
  summarize(
    sample_mean = mean(change),
    sample_sd = sd(change),
    sample_n = n()
  ) %>%
  mutate(
    error = qt(0.975, df = sample_n - 1) * sample_sd / sqrt(sample_n),
    ci_low = sample_mean - error,
    ci_high = sample_mean + error
  )

#########################
# Self Focus: Child Object
#########################
reportedValues = reported_descriptives$self_focus$child_change
obtainedValues = filter(df.object.prime_type.summary, object == "child", prime_type == "self")
## Mean
compareValues(
  reportedValues$mean,
  obtainedValues$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues$ci_low,
  obtainedValues$ci_low
)

compareValues(
  reportedValues$ci_high,
  obtainedValues$ci_high
)

#########################
# Self Focus: Experimenter Object
#########################
reportedValues_self_experimenter = reported_descriptives$self_focus$experimenter_change
obtainedValues_self_experimenter = filter(df.object.prime_type.summary, 
                                          object == "experimenter", prime_type == "self")
## Mean
compareValues(
  reportedValues_self_experimenter$mean,
  obtainedValues_self_experimenter$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_self_experimenter$ci_low,
  obtainedValues_self_experimenter$ci_low
)

compareValues(
  reportedValues_self_experimenter$ci_high,
  obtainedValues_self_experimenter$ci_high
)

#########################
# Other Focus: Child Object
#########################
reportedValues_other_child = reported_descriptives$other_focus$child_change
obtainedValues_other_child = filter(df.object.prime_type.summary, 
                                          object == "child", prime_type == "other")
## Mean
compareValues(
  reportedValues_other_child$mean,
  obtainedValues_other_child$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_other_child$ci_low,
  obtainedValues_other_child$ci_low
)

compareValues(
  reportedValues_other_child$ci_high,
  obtainedValues_other_child$ci_high
)

#########################
# Other Focus: Experimenter Object
#########################
reportedValues_other_experimenter = reported_descriptives$other_focus$experimenter_change
obtainedValues_other_experimenter = filter(df.object.prime_type.summary, 
                                          object == "experimenter", prime_type == "other")
## Mean
compareValues(
  reportedValues_other_experimenter$mean,
  obtainedValues_other_experimenter$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_other_experimenter$ci_low,
  obtainedValues_other_experimenter$ci_low
)

compareValues(
  reportedValues_other_experimenter$ci_high,
  obtainedValues_other_experimenter$ci_high
)

#########################
# Neutral Focus: Child Object
#########################
reportedValues_neutral_child = reported_descriptives$neutral_focus$child_change
obtainedValues_neutral_child = filter(df.object.prime_type.summary, 
                                          object == "child", prime_type == "neutral")
## Mean
compareValues(
  reportedValues_neutral_child$mean,
  obtainedValues_neutral_child$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_neutral_child$ci_low,
  obtainedValues_neutral_child$ci_low
)

compareValues(
  reportedValues_neutral_child$ci_high,
  obtainedValues_neutral_child$ci_high
)

#########################
# Neutral Focus: Experimenter Object
#########################
reportedValues_neutral_experimenter = reported_descriptives$neutral_focus$experimenter_change
obtainedValues_neutral_experimenter = filter(df.object.prime_type.summary, 
                                          object == "experimenter", prime_type == "neutral")
## Mean
compareValues(
  reportedValues_neutral_experimenter$mean,
  obtainedValues_neutral_experimenter$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_neutral_experimenter$ci_low,
  obtainedValues_neutral_experimenter$ci_low
)

compareValues(
  reportedValues_neutral_experimenter$ci_high,
  obtainedValues_neutral_experimenter$ci_high
)

```


```{r descriptives_prime_type}
df.object.prime_type.summary <- df.tidy %>%
  spread(scoringPeriod, response) %>%
  group_by(prime_type) %>%
  summarize(
    sample_mean = mean(change),
    sample_sd = sd(change),
    sample_n = n()
  ) %>%
  mutate(
    error = qt(0.975, df = sample_n - 1) * sample_sd / sqrt(sample_n),
    ci_low = sample_mean - error,
    ci_high = sample_mean + error
  )

#########################
# Self Focus (collapse across objects)
#########################
reportedValues_selfPrime = reported_descriptives$picture_types$self
obtainedValues_selfPrime = filter(df.object.prime_type.summary, prime_type == "self")
## Mean
compareValues(
  reportedValues_selfPrime$mean,
  obtainedValues_selfPrime$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_selfPrime$ci_low,
  obtainedValues_selfPrime$ci_low
)

compareValues(
  reportedValues_selfPrime$ci_high,
  obtainedValues_selfPrime$ci_high
)

#########################
# Other Focus (collapse across objects)
#########################
reportedValues_otherPrime = reported_descriptives$picture_types$other
obtainedValues_otherPrime = filter(df.object.prime_type.summary, prime_type == "other")
## Mean
compareValues(
  reportedValues_otherPrime$mean,
  obtainedValues_otherPrime$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_otherPrime$ci_low,
  obtainedValues_otherPrime$ci_low
)

compareValues(
  reportedValues_otherPrime$ci_high,
  obtainedValues_otherPrime$ci_high
)

#########################
# Neutral Focus (collapse across objects)
#########################
reportedValues_neutralPrime = reported_descriptives$picture_types$neutral
obtainedValues_neutralPrime = filter(df.object.prime_type.summary, prime_type == "neutral")
## Mean
compareValues(
  reportedValues_neutralPrime$mean,
  obtainedValues_neutralPrime$sample_mean
)

## CIs (Note that these be off if the mean is off)
compareValues(
  reportedValues_neutralPrime$ci_low,
  obtainedValues_neutralPrime$ci_low
)

compareValues(
  reportedValues_neutralPrime$ci_high,
  obtainedValues_neutralPrime$ci_high
)
```


### Inferential statistics

> To examine the effects of priming on value-change for the two identical endowment toys, a mixed ANCOVA was conducted. Toy owner (child or experimenter) was entered as a repeated measures factor and picture type (self-focus, other- focus, neutral-focus) and gender were entered as a between sub- jects factors. Additionally, child age was normalized and entered as a covariate into the model.

Main results (Section 2.3):

> We found a significant interaction between picture construction condition and toy owner (F(2, 53) = 4.83, p = 0.01, View the MathML source).

```{r}
ezANOVA(
  df.tidy %>%
    filter(scoringPeriod == "change", object != "neutral"),
  dv = response,
  wid = participant_id,
  within = .(object),
  between = .(prime_type, gender),
  between_covariates = age_normalized
)


``` 

## Step 5: Conclusion

```{r}
```

[Please also include a brief text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
